### 2014-06-27 alex/2020.Rmd

Not much correlation between scores and out of school study hours
```{r outhours, cache=TRUE, tidy=FALSE}
qplot(x = OUTHOURS, y = math, 
      data = student2012 %>% 
        select(OUTHOURS, math) %>% 
        filter(!is.na(OUTHOURS)), 
      alpha = I(0.1)) + stat_smooth()
qplot(x = OUTHOURS, y = read, 
      data = student2012 %>% 
        select(OUTHOURS, read) %>% 
        filter(!is.na(OUTHOURS)), 
      alpha = I(0.1) ) + stat_smooth()
qplot(x = OUTHOURS, y = sci, 
      data = student2012 %>% 
        select(OUTHOURS, sci) %>% 
        filter(!is.na(OUTHOURS)), 
      alpha = I(0.1) ) + stat_smooth()
```

>>>>

Not much correlation between scores and out of school study hours
```{r outhours, cache=TRUE, tidy=FALSE}
qplot(x = OUTHOURS, y = math, 
      data = student2012 %>% 
        select(OUTHOURS, math) %>% 
        filter(!is.na(OUTHOURS)), 
      alpha = I(0.05)) + stat_smooth()
qplot(x = OUTHOURS, y = read, 
      data = student2012 %>% 
        select(OUTHOURS, read) %>% 
        filter(!is.na(OUTHOURS)), 
      alpha = I(0.05) ) + stat_smooth()
qplot(x = OUTHOURS, y = sci, 
      data = student2012 %>% 
        select(OUTHOURS, sci) %>% 
        filter(!is.na(OUTHOURS)), 
      alpha = I(0.05)) + stat_smooth()
```
